---
title: "Preparing Air Quality"
---

# Open libraries
```{r}
library(forecast)
library(ggplot2)
library(fpp2)
library(readr)
library(plyr)
library(lubridate)
library(dplyr)
library(xts)
library(TSstudio)
```

# Join Data
```{r}
#2001
a2001 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2001.csv")
a2001$MXY <- NULL
a2001$NOx <- NULL
a2001$OXY <- NULL
a2001$PXY <- NULL
```

```{r}
# 2002
a2002 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2002.csv")
a2002$MXY <- NULL
a2002$NOx <- NULL
a2002$OXY <- NULL
a2002$PXY <- NULL
atotal<-rbind(a2001,a2002)
```

```{r}
# 2003
a2003 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2003.csv")
a2003$MXY <- NULL
a2003$NOx <- NULL
a2003$OXY <- NULL
a2003$PXY <- NULL
atotal<-rbind(atotal,a2003)
```

```{r}
# 2004
a2004 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2004.csv")
a2004$MXY <- NULL
a2004$NOx <- NULL
a2004$OXY <- NULL
a2004$PXY <- NULL
a2004$PM25 <- NULL
atotal<-rbind(atotal,a2004)
```

```{r}
# 2005
a2005 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2005.csv")
a2005$MXY <- NULL
a2005$NOx <- NULL
a2005$OXY <- NULL
a2005$PXY <- NULL
a2005$PM25 <- NULL
atotal<-rbind(atotal,a2005)
```

```{r}
# 2006
a2006 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2006.csv")
a2006$MXY <- NULL
a2006$NOx <- NULL
a2006$OXY <- NULL
a2006$PXY <- NULL
a2006$PM25 <- NULL
atotal<-rbind(atotal,a2006)
```

```{r}
# 2007
a2007 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2007.csv")
a2007$MXY <- NULL
a2007$NOx <- NULL
a2007$OXY <- NULL
a2007$PXY <- NULL
a2007$PM25 <- NULL
atotal<-rbind(atotal,a2007)
```

```{r}
# 2008
a2008 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2008.csv")
a2008$MXY <- NULL
a2008$NOx <- NULL
a2008$OXY <- NULL
a2008$PXY <- NULL
a2008$PM25 <- NULL
atotal<-rbind(atotal,a2008)
```

```{r}
# 2009
a2009 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2009.csv")
a2009$MXY <- NULL
a2009$NOx <- NULL
a2009$OXY <- NULL
a2009$PXY <- NULL
a2009$PM25 <- NULL
atotal<-rbind(atotal,a2009)
```

```{r}
# 2010
a2010 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2010.csv")
a2010$MXY <- NULL
a2010$NOx <- NULL
a2010$OXY <- NULL
a2010$PXY <- NULL
a2010$PM25 <- NULL
atotal<-rbind(atotal,a2010)
```

```{r}
# 2011
a2011 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2011.csv")
a2011$PM25 <- NULL
a2011$NO <- NULL
atotal<-rbind(atotal,a2011)
```

```{r}
# 2012
a2012 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2012.csv")
a2012$PM25 <- NULL
a2012$NO <- NULL
atotal<-rbind(atotal,a2012)
```

```{r}
# 2013
a2013 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2013.csv")
a2013$PM25 <- NULL
a2013$NO <- NULL
atotal<-rbind(atotal,a2013)
```

```{r}
# 2014
a2014 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2014.csv")
a2014$PM25 <- NULL
a2014$NO <- NULL
atotal<-rbind(atotal,a2014)
```

```{r}
# 2015
a2015 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2015.csv")
a2015$PM25 <- NULL
a2015$NO <- NULL
atotal<-rbind(atotal,a2015)
```

```{r}
# 2016
a2016 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2016.csv")
a2016$PM25 <- NULL
a2016$NO <- NULL
atotal<-rbind(atotal,a2016)
```

```{r}
# 2017
a2017 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2017.csv")
a2017$PM25 <- NULL
a2017$NO <- NULL
a2017$CH4 <- NULL
a2017$NOx <- NULL
atotal<-rbind(atotal,a2017)
```

```{r}
# 2018
a2018 <- read_csv("~/OneDrive/Documentos/BDBA/2/2.1/Programming DMA/Project/air-quality-madrid/csvs_per_year/csvs_per_year/madrid_2018.csv")
a2018$PM25 <- NULL
a2018$NO <- NULL
a2018$CH4 <- NULL
a2018$NOx <- NULL
atotal<-rbind(atotal,a2018)
atotal <- as.data.frame(atotal)
```

# Deal with NA
```{r}
#Transform NA as 0
atotal[is.na(atotal)] <- 0
summary(atotal)
str(atotal)
```

# Select NO_2
```{r}
NO_2total <- atotal
NO_2total$BEN <- NULL
NO_2total$CO <- NULL
NO_2total$EBE <- NULL
NO_2total$NMHC <- NULL
NO_2total$O_3 <- NULL
NO_2total$PM10 <- NULL
NO_2total$SO_2 <- NULL
NO_2total$TCH <- NULL
NO_2total$TOL <- NULL
```

# Configurate date variable
```{r}
NO_2total$Date <- as.Date(NO_2total$date)
NO_2total$Time <- format(NO_2total$date,"%H:%M:%S")
NO_2total$date <- NULL
```

# Divide into stations
```{r}
Pza_Espana <- NO_2total[NO_2total$station == 28079004,]
Casa_Campo <- NO_2total[NO_2total$station == 28079024,]
```

# Plaza Espa?a
#Checking the structure of one of the datasets Pza_Espana
```{r}
str(Pza_Espana)
```

#Convert into weeks
```{r}
# Converting the initial date into date
date <- as.Date(as.character(Pza_Espana$Date), "%Y-%m-%d")
#Leaving the date as an index and the NO_2 as the variable of interest: extended time series
Pza_Espana_xts <- xts(Pza_Espana$NO_2, date)
```

#Check structure, length and number of columns
```{r}
str(Pza_Espana_xts)
length(Pza_Espana_xts)
ncol(Pza_Espana_xts)
```

#Convert the extended time series into weekly averaging the values
```{r}
#Set up the end of the week for the time series
week.end.pe <- endpoints(Pza_Espana_xts, on = "weeks")

#Transform the data into weekly data using averages
Pza_Espana_weekly <- period.apply(Pza_Espana_xts, INDEX = week.end.pe, FUN = mean)
```

#Convert the xts class to a ts class
```{r}
#Convert xts to ts
Pza_Espana_weekly_ts <- xts_to_ts(Pza_Espana_weekly, start = as.Date("2001-01-07"), frequency = 52)

#head() and tail() will also show the attributes, focus on the first values although it will make it a bit slower to calculate all of them
```

#Check the conversion and plot the ts()
```{r}
#Plot the ts, seasonality, subseries and display
autoplot(Pza_Espana_weekly_ts)
ggseasonplot(Pza_Espana_weekly_ts)
ggsubseriesplot(Pza_Espana_weekly_ts)
ggtsdisplay(Pza_Espana_weekly_ts)
```

#Create a train and a test set
```{r}
#In this case your second number in "end" and "start" is a week within the year! so from 1-52
train.Pza_Espana <-window(Pza_Espana_weekly_ts, end = c(2016, 21))
test.Pza_Espana <-window(Pza_Espana_weekly_ts, start = c(2016,22))

#Plot both to see that it works properly
autoplot(train.Pza_Espana)
autoplot(test.Pza_Espana)
```


# Casa de Campo
#Checking the structure of one of the datasets Casa_Campo
```{r}
str(Casa_Campo)
```

#Convert into weeks
```{r}
# Converting the initial date into date
date <- as.Date(as.character(Casa_Campo$Date), "%Y-%m-%d")
#Leaving the date as an index and the NO_2 as the variable of interest: extended time series
Casa_Campo_xts <- xts(Casa_Campo$NO_2, date)
```

#Check structure, length and number of columns
```{r}
str(Casa_Campo_xts)
length(Casa_Campo_xts)
ncol(Casa_Campo_xts)
```

#Convert the extended time series into weekly averaging the values
```{r}
#Set up the end of the week for the time series
week.end.cc <- endpoints(Casa_Campo_xts, on = "weeks")

#Transform the data into weekly data using averages
Casa_Campo_weekly <- period.apply(Casa_Campo_xts, INDEX = week.end.cc, FUN = mean)
```

#Convert the xts class to a ts class
```{r}
#Convert xts to ts
Casa_Campo_weekly_ts <- xts_to_ts(Casa_Campo_weekly, start = as.Date("2001-01-07"), frequency = 52)

#head() and tail() will also show the attributes, focus on the first values although it will make it a bit slower to calculate all of them
```

#Check the conversion and plot the ts()
```{r}
#Plot the ts, seasonality, subseries and display
autoplot(Casa_Campo_weekly_ts)
ggseasonplot(Casa_Campo_weekly_ts)
ggsubseriesplot(Casa_Campo_weekly_ts)
ggtsdisplay(Casa_Campo_weekly_ts)
```

#Create a train and a test set
```{r}
#In this case your second number in "end" and "start" is a week within the year! so from 1-52
train.Casa_Campo <-window(Casa_Campo_weekly_ts, end = c(2016, 21))
test.Casa_Campo <-window(Casa_Campo_weekly_ts, start = c(2016,22))

#Plot both to see that it works properly
autoplot(train.Casa_Campo)
autoplot(test.Casa_Campo)
```